What We Eval in the Shadows

### 2021-08-13 paper/main.tex
Update 6.boilerplate
Update 6.boilderplate

\paragraph{Boilerplate Removal}
A variant of code generation is to let users write compact code that is expended
via \eval and \k{match.call}. The example uses \k{match.call} to access
the expression with which the function is called. The next three lines construct
a call to \k{stats::model.frame} with argument text of parameters
\k{'formula'}, \k{'data'}, and \k{'weights'}. Then, the call expression
is evaluated in the parent environment. The use of \k{match.call}, avoids
repeated use of \k{substitute} for extracting the argument expressions. This
setup is also extensible as new parameter names can be easily added.

@@

>>>>

\paragraph{Boilerplate Removal} 
A variant of code generation is to let users write compact code that is
expended via \eval and \k{match.call}. The example uses \k{match.call} to
access the expression with which the function is called. The next three lines
construct a call to \k{stats::model.frame} with argument text of parameters
\k{'formula'}, \k{'data'}, and \k{'weights'}. Then, the call expression is
evaluated in the parent environment. The use of \k{match.call}, avoids repeated
use of \k{substitute} for extracting the argument expressions. It is extensible
as new parameter names can be easily added. This example illustrates one of the
most recurring usage of \eval that is used by the majority of packages that do
statistical modeling.

@@

This combination of \k{match.call} and \eval to pass most of the call to
another function is also used to created wrappers. For example, the
\k{write.csv} uses it to forward most of the parameters to the more general
\k{write.table} function, only setting the CSV-related parameters:

\begin{minipage}{.95\textwidth}
  \medskip\underline{\c{base::write.csv}:}
\begin{lstlisting}
function (...)
{
    Call <- match.call(expand.dots = TRUE)
    Call$sep <- ","
    Call$dec <- "."
    Call$qmethod <- "double"
    Call[[1L]] <- as.name("write.table")
    eval.parent(Call)
}
\end{lstlisting}\medskip
\end{minipage}

The most probable reason for this is to ease maintenance of such
wrappers.\footnote{This was speculated by the Brian Ripley, the author of the
function, in a private conversation.} Wrapping functions in R is somewhat
harder than in other languages because of the default arguments, the varargs
and is missing arguments.
